Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-17 paper/sec-pileup.tex
More work on the PU section

>>>>

Next we consider how PU affects kinematical distributions
in the boosted category.
%
In the following we assess the effect of PU in four additional
distributions: the transverse momentum of the leading Higgs
candidate, $p_t^{h_1}$, the invariant mass of the di-Higgs system
$m_{hh}$, and two substructure variables, the subjetiness
$\tau_{21}$ and $D_2$ of the leading Higgs candidate.
%
This comparison is illustrated in Fig.~\ref{fig:mHH_PU}.
%
Therefore, as we can see, the substructure variables, which
as demonstrated before carry a very substantial
discrimination power, are relatively unaffected by PU.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \vspace{-1cm}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_bst_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_bst_comp.pdf}
  \caption{\small
    Comparison of the transverse momentum $p_T^h$ of the leading
    Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
    of the di-Higgs system (lower plots) in the resolved
    (left plots) and boosted (right plots) categories,
    without PU and with $\la n_{PU}\ra=80$ subtracted with SoftKiller.
}
\label{fig:mHH_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

Next we assess the impact of PU in some of the substructure variables
used as input to the MVA in the boosted category.
%
In particular $m_{hh}$, and two substructure variables, the subjetiness
$\tau_{21}$ and $D_2$ of the leading Higgs candidate.
%
This comparison is illustrated in Fig.~\ref{fig:substructure_PU}.
%
Therefore, as we can see, the substructure variables, which
as demonstrated before carry a very substantial
discrimination power, are relatively unaffected by PU.

Up to know we have restricted ourselves to the study of the impact of PU
on signal distributions.
%
We now assess how the signal over background discrimination can be affected
in the presence of realistic PU conditions.
